学術論文

### 2022-07-08 articles.Rmd
update

@@

- [38] Somatori, K. & Kunisato, Y. (in press) Metacognitive Ability and the Precision of Confidence. Frontiers in Human Neuroscience, section Cognitive Neuroscience [Link](https://www.frontiersin.org/articles/10.3389/fnhum.2022.706538/abstract)

- [37] Hasegawa, A., Oura, S., Yamamoto, T., Kunisato, Y., Matsuda, Y., & Adachi, M. (in press) Causes and consequences of stress generation: Longitudinal associations of negative events, aggressive behaviors, rumination, and depressive symptoms. Current Psychology

>>>>

- [41] Hasegawa, A., Oura, S., Yamamoto, T., Kunisato, Y., Fukui, Y.(in press) Preliminary validation of the self-report measure assessing experiences of negative independent and dependent event frequency in japanese university students. Journal of Rational-Emotive & Cognitive-Behavior Therapy.

- [40] PSACR-001. (in press).
In COVID-19 health messaging, loss framing increases anxiety without concomitant benefits: Experimental evidence from 84 countries. Affective Science.

@@

### 2022

- [38] Somatori, K. & Kunisato, Y. (2022) Metacognitive Ability and the Precision of Confidence. Frontiers in Human Neuroscience, section Cognitive Neuroscience [Link](https://www.frontiersin.org/articles/10.3389/fnhum.2022.706538/abstract)

- [37] Hasegawa, A., Oura, S., Yamamoto, T., Kunisato, Y., Matsuda, Y., & Adachi, M. (2022) Causes and consequences of stress generation: Longitudinal associations of negative events, aggressive behaviors, rumination, and depressive symptoms. Current Psychology
